The {\sc VSPEC} code: Spectroscopic phase curves of 3D exoplanet models in the presence of stellar variability

### 2024-06-04 src/tex/ms.tex
Many bugfixes. The expectation is the the GHA should now be sucessfull

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

@@

We model granulation as a global process, and its effects are computed after the effects of spots and faculae.
Of the remaining ``quiet'' photosphere (i.e. the regions not covered in spots of faculae), a fraction is computed to be part of the cool
inter-granule surface. The surface coverage of the cool region at any given time is computed by a Gaussian process (GP) using
the \sc{tinygp} package \citep{foreman-mackey2024} following the methodology of \citet{gordon2020}.
The GP uses a custom kernel function based on a power spectrum \citep{anderson1990,kallinger2014} to produce random changes in the coverage.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{sphx_glr_plot_gj1214b_kempton23_006.png}
    \caption{
        MIRI phase curves for GJ 1214b binned by wavelength. Compare to \citet{kempton2023} Extended Data Figure 1.
        While the addition of stellar variability does have a visible effect on the lightcurve, it is much smaller than the thermal emission by the exoplanet.
        }
    \script{kempton23.py}
    \label{fig:gj1214b}
\end{figure}

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}

@@

We model granulation as a global process, and its effects are computed after the effects of spots and faculae.
Of the remaining ``quiet'' photosphere (i.e. the regions not covered in spots of faculae), a fraction is computed to be part of the cool
inter-granule surface. The surface coverage of the cool region at any given time is computed by a Gaussian process (GP) using
the {\sc tinygp} package \citep{foreman-mackey2024} following the methodology of \citet{gordon2020}.
The GP uses a custom kernel function based on a power spectrum \citep{anderson1990,kallinger2014} to produce random changes in the coverage.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/kempton23.pdf}
    \caption{
        MIRI phase curves for GJ 1214b binned by wavelength. Compare to \citet{kempton2023} Extended Data Figure 1.
        While the addition of stellar variability does have a visible effect on the lightcurve, it is much smaller than the thermal emission by the exoplanet.
        }
    \script{kempton23.py}
    \label{fig:gj1214b}
\end{figure}
